% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./profile}
\name{}{LAI Kwun Hang (Adrian)}
\position{Phd Candidate}
%\address{235, World Cup buk-ro, Mapo-gu, Seoul, 03936, Republic of Korea}

\mobile{(+852) 9171-2155}
\email{adrian.k.h.lai@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{Adriankhl}
\linkedin{adrian-k-h-lai}
\orcid{0000-0003-0446-119X}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``We are all in the gutter, but some of us are looking at the stars"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Our Hong Kong Foundation}
  {Hong Kong}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Researcher/Assistant Researcher}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}%\today}
  {}%Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}



I am writing to express my strong interest in the ``Researcher/Assistant Researcher'' position at Our Hong Kong Foundation. As a social scientist with a strong technical background, I am eager to contribute my unique blend of expertise to support public policy research and development in Hong Kong.

My academic journey commenced in the field of physics. During my master's research in black hole physics, I observed issues within academia that left me dissatisfied with the existing academic system. This realization led me to pursue a Ph.D. in social science, where I focused on studying the academic system itself. A significant portion of my research specialized in the academic funding system, examining biases in funding allocations and proposing ways to enhance the system's efficiency. Additionally, I have gained extensive exposure to the ongoing reform of academic research in Europe, which emphasizes alternative research outcomes, such as public engagement and software, to drive a more relevant societal impact. Given that the technology industry is becoming a core sector in Hong Kong, with academia-industry partnerships playing a crucial role, I am confident that I can make meaningful contributions to technology and innovation policy in Hong Kong.

In addition to my personal knowledge, I can serve as a bridge between the team in Hong Kong and my current institute, the Centre for Science and Technology Studies (CWTS) in Leiden, the Netherlands. CWTS possesses an extensive database encompassing academic publications, patents, social media, and policy documents, which is invaluable for science policy research. Moreover, researchers at CWTS possess expertise in studying science policy across different countries in Europe, the Americas, and Asia. Notably, CWTS enjoys a strong reputation in China, attracting numerous Chinese scholars and fostering collaborative projects on science policy in China. Leveraging these resources and networks, I can contribute to analyzing Hong Kong's potential learnings from other countries and aligning Hong Kong's policies with those of China.

My academic training and experience have also equipped me with solid research skills across different domains. With a strong quantitative background, I am proficient in applying state-of-the-art data analytical methods and modeling tools. As part of my Ph.D. and a personal interest, I have collaboratively and independently developed several software, including a social simulation framework and an educational game. Recognizing the increasing importance of software in social science research, I am adept at supporting the development of research software either independently or in collaboration with other software developers. Throughout my Ph.D., I have collaborated with individuals from diverse backgrounds, including researchers, policymakers, administrators, and engineers, demonstrating my ability to work effectively with different stakeholders and complement each other's weaknesses. Additionally, I have actively engaged in various social events, such as presenting at conferences and organizing workshops, showcasing both my technical and soft skills. These attributes affirm my capability to excel within the foundation.

Thank you for considering my application. I am excited about the opportunity to apply my expertise to research and shape the policies of my home city, Hong Kong. I eagerly anticipate the chance to discuss my qualifications further in an interview.

%\lettersection{Why Me?}

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
