% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./profile}
\name{}{LAI Kwun Hang (Adrian)}
\position{Phd Candidate}
%\address{235, World Cup buk-ro, Mapo-gu, Seoul, 03936, Republic of Korea}

\mobile{(+852) 9171-2155}
\email{adrian.k.h.lai@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{Adriankhl}
\linkedin{adrian-k-h-lai}
\orcid{0000-0003-0446-119X}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``We are all in the gutter, but some of us are looking at the stars"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {The Hong Kong Jockey Club}
  {Hong Kong}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for (Assistant) Manager, Charities (Healthy Community – General)}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}%\today}
  {}%Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}


I am writing to express my strong interest in the "(Assistant) Manager, Charities (Healthy Community – General)" position at the Hong Kong Jockey Club. As a social scientist specializing in research funding, I am eager to contribute my unique blend of expertise to support the projects at the Charities Department.

My academic journey commenced in the field of physics. During my master's research in black hole physics, I observed issues within academia that left me dissatisfied with the existing academic system. This realization led me to pursue a Ph.D. in social science, where I focused on studying the academic system itself. A significant portion of my research specialized in the academic funding system, examining biases in funding allocations and proposing ways to enhance the system's efficiency. Additionally, I have gained extensive exposure to the ongoing reform of academic research in Europe, which emphasizes alternative research outcomes, such as public engagement and software, to drive a more relevant societal impact. This exposure has given me valuable insights into best practices and innovative approaches in research funding.

In addition to my academic knowledge, I can serve as a bridge between the team in Hong Kong and other relevant organizations. At the Centre for Science and Technology Studies (CWTS), where I am currently a researcher, we specialize in studying science policy across different countries. As part of my work under the Research on Research Institute, I have collaborated with international stakeholders, including funding agencies, universities, and policymakers, to analyze research funding systems and identify areas of improvement. Leveraging these experiences and networks, I am confident in my ability to contribute to the analysis of potential learnings from other funding agencies to enhance the funding system at the Hong Kong Jockey Club.


Moreover, my academic training and experience have equipped me with a diverse set of technical and soft skills that are crucial for success in this role. With a strong quantitative background, I am proficient in applying state-of-the-art data analytical methods and modeling tools to extract meaningful insights from complex datasets. Throughout my Ph.D., I have developed several software projects, both collaboratively and independently. My experience working with stakeholders from various backgrounds has honed my ability to communicate effectively and build strong relationships. I have actively engaged in various social events, such as presenting at conferences and organizing workshops, showcasing both my technical and soft skills. This skill set will allow me to work seamlessly with the diverse team at the Hong Kong Jockey Club and contribute to the success of the Charities Department.

Thank you for considering my application. Currently, I am in Hong Kong to complete my thesis. I am excited about the opportunity to further discuss my qualifications in an interview.

%\lettersection{Why Me?}

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
