% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./profile}
\name{}{LAI Kwun Hang (Adrian)}
\position{Phd Candidate}
%\address{235, World Cup buk-ro, Mapo-gu, Seoul, 03936, Republic of Korea}

\mobile{(+852) 9171-2155}
\email{adrian.k.h.lai@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{Adriankhl}
\linkedin{adrian-k-h-lai}
\orcid{0000-0003-0446-119X}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``We are all in the gutter, but some of us are looking at the stars"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Faculty of Arts}
  {University of Hong Kong}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Senior Software Engineer/Software Engineer (at the rank of IT Manager/IT Officer)}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}%\today}
  {}%Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing to express my enthusiastic interest in the "Software Engineer" position at Hong Kong University. As a social scientist and software developer, I am deeply passionate about creating software solutions that cater to the needs of the Social Sciences and Humanities. As I am finishing my Ph.D., I am excited about the prospect of leveraging my skills to contribute to the Arts Technology Lab and make a meaningful impact in this field.

My academic journey has been a unique blend of physics, astrophysics, and computational social science, providing me with a diverse and robust skill set that aligns well with the role. I have a proven track record in multiple technical domains, including proficiency in C, Python, SQL, Linux systems, and simulations. One of my flagship projects is a sophisticated agent-based simulation framework and a game written Kotlin. The framework, designed with a strong foundation in physics, includes proper design patterns, extensive unit/integration tests, and comprehensive documentation. This project showcases my ability to independently translate complex academic ideas into well-designed software products.

In addition to my academic pursuits, I am an active contributor to open-source projects. I regularly contribute bug fixes and introduce new features to various software that I use on a daily basis. These experiences have sharpened my skills in learning, debugging, and collaborating with unfamiliar technologies and codebases, demonstrating my readiness to tackle new challenges head-on.

While my educational background may not be in computer science, I have consistently demonstrated my ability to self-study and acquire necessary computer science knowledge whenever required. For instance, during the development of my simulation framework, I studied algorithm optimization and coroutines to enhance its performance. I am confident in my aptitude to quickly grasp and apply any new knowledge that is relevant to the work at the Arts Technology Lab.

Throughout my academic journey, I have excelled in diverse, cross-cultural collaborations, honing my teamwork and communication skills. I have taken the initiative to organize technical workshops for non-technical people and actively participate in events promoting open science. These experiences have equipped me with the ability to thrive in collaborative environments and contribute effectively to cross-functional teams.

Thank you for considering my application. I am eager for the opportunity to discuss my qualifications further in an interview and explore how my skills and passion align with the exciting work at Hong Kong University. I am confident that my unique blend of academic expertise and software development skills would make me a valuable addition to the Arts Technology Lab.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
