% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./profile}
\name{}{LAI Kwun Hang (Adrian)}
\position{Phd Candidate}
%\address{235, World Cup buk-ro, Mapo-gu, Seoul, 03936, Republic of Korea}

\mobile{(+852) 9171-2155 / (+31) 6-2184-1392}
\email{adrian.k.h.lai@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{Adriankhl}
\linkedin{adrian-k-h-lai}
\orcid{0000-0003-0446-119X}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``We are all in the gutter, but some of us are looking at the stars"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {The Chinese University of Hong Kong Library}
  {Hong Kong}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Assistant Librarian I (carrying the job title of ‘Open Science Librarian’) (240000AN)}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}%\today}
  {}%Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing to express my strong interest in the "Assistant Librarian I (carrying the job title of 'Open Science Librarian')" position at the Chinese University of Hong Kong (CUHK) Library. I am particularly excited about this opportunity because it aligns perfectly with my desire to contribute to the advancement of open science practices in my alma mater and my home country.

My current institute, the Centre for Science and Technology Studies (CWTS) at Leiden University, is renowned for its expertise in science studies research and has been at the forefront of open science initiatives, such as ``Plan S'' and UNESCO open science working groups. Through my association with CWTS, I have gained extensive exposure to various facets of open science. Moreover, CWTS has strong connections with science policy scholars in mainland China. I am happy to serve as a bridge between CUHK Library, CWTS, Chinese scholars, and other open science organizations.

Although my primary research focus has been on modeling the academic system rather than open science specifically, I have actively participated in several open science-related projects and events. For instance, I have been part of the CWTS working group responsible for the transition to open research information, utilizing databases like OpenAlex. Additionally, I played a key role in testing and managing the open access and open peer review platform, Orvium, for the International Conference on Science, Technology, and Innovation Indicators in 2023. Furthermore, I have contributed to open source software projects and shared my experiences in open source research software at various conferences and meetings. These experiences underscore my commitment to practicing and promoting open science.

My interdisciplinary academic background in physics, mathematics, social science, and software development equips me with a broad understanding of the needs of academic staff across diverse disciplines. Furthermore, I have successfully organized events and workshops involving administrative and library staff at Leiden University, demonstrating my ability to collaborate effectively with different stakeholders. Additionally, my fluency in English, Putonghua, and Cantonese enables me to work seamlessly with local, mainland Chinese, and international individuals.

One of my key strengths lies in my strong IT skills. I possess extensive experience in analyzing scientific and social science data, and I have actively contributed to various open source software projects using multiple programming languages. Furthermore, I have developed a simulation game from scratch, which has allowed me to explore the potential of game development in promoting open science and citizen science. An example of this is the ``Software Horror Escape Room'' game developed by the library staff in the Netherlands regarding the publication of academic software. I believe my IT skills could be valuable assets in providing digital services, improving open science infrastructure and engaging with the academic community.

Although I may not have professional experience as a librarian, my unique combination of experiences and skills sets me apart for this position. I am eager to learn any additional traditional librarian skills that may be required. Thank you for considering my application. Currently, I am in Hong Kong until at least early April. I look forward to the opportunity to discuss my qualifications further.

%\lettersection{Why Me?}

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
