%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {On social simulation in 4D relativistic spacetime} % Role
    {Social Simulation Conference} % Event
    {Milan, Italy} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Explained the mathematical and algorithmic details of my simulation framework.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Relativitization: a turn-based strategy game in 4D relativistic spacetime} % Role
    {Social Simulation Conference} % Event
    {Milan, Italy} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Poster presentation about my turn-based strategy game.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Relativitization: a social simulation framework in 4D relativistic spacetime} % Role
    {International conference of computational science} % Event
    {London, United Kingdom} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Poster presentation about my interstellar social simulation framework.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Behavioural models of funding applications} % Role
    {Funded and Unfunded Science: Academic Inequalities and Epistemic Gaps} % Event
    {Prague, Czech Republic} % Location
    {2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced my research on behavioural models of funding applicants.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Constructing models of academic funding system: relation between the amount of funding and the efficiency} % Role
    {The 18th International Conference of the International Society for Scientometrics and Informetrics} % Event
    {Belgium (Virtual)} % Location
    {2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Presented my research on game theoretical models and agent-based models of the academic funding system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Challenges in Using Bibliometric Indicators to Assess Peer Review Decisions: A Simulation Model} % Role
    {PEERE International Conference on Peer Review 2020} % Event
    {Spain (Virtual)} % Location
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Illustrated a potential problem when using bibliometric indicators to assess peer reviews.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Discovering intermediate‑mass black hole lenses through gravitational wave lensing} % Role
    {Gravity and Cosmology 2018} % Event
    {Yukawa Institute for Theoretical Physics, Kyoto University, Japan} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced my research on utilizing gravitational waves lensing to search for intermediate‑mass black holes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Gravitational lensing of gravitational waves} % Role
    {First CUHK Physics Student Conference 2017} % Event
    {The Chinese University of Hong Kong, China} % Location
    {2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced gravitational lensing of gravitational waves.}
        \item {Best speaker of the first CUHK Physics Student Conference.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
