%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research/Work Highlights}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Relativitization: an agent-based simulation framework in 4D, relativistic spacetime} % Research project
    {Research software/game development} % Research organization
    {Leiden, The Netherlands} % Location
    {2021 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programming language: Kotlin.}
        \item {Create a parallel computational framework for social scientists to simulate interstellar agent-based models.}
        \item {Build models to demonstrate the effect relativistic physics on interstellar societies.}
        \item {Develop a video game for PC and Android on top of the framework.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Criteria Project} % Research project
    {Research on Research Institute (RORI)} % Research organization
    {Leiden, The Netherlands} % Location
    {2020 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programming language: SQL and Python.}
        \item {Construct Bayesian models on the relation between the gender bias and criteria of funding applications.}
        \item {Perform data cleaning and analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Gravitational waves modeling and data analysis} % Research project
    {LIGO Scientific Collaboration (LSC) Projects} % Research organization
    {Hong Kong, China} % Location
    {2016 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programming language: C and Python.}
        \item {Proposed methods to constrain black-hole horizon effects.}
        \item {Ran simulations of detecting intermediate-mass black hole by gravitational wave lensing.}
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%    {Majorana Stellar Representation of Quantum Entanglement} % Research project
%    {Undergraduate Research Project} % Research organization
%    {Hong Kong, China} % Location
%    {2015} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Visualized spin-1/2 particle states by Majorana stars.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
