% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./profile}
\name{}{LAI Kwun Hang (Adrian)}
\position{Phd Candidate}
%\address{235, World Cup buk-ro, Mapo-gu, Seoul, 03936, Republic of Korea}

\mobile{(+31) 6-2184-1392}
\email{adrian.k.h.lai@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{Adriankhl}
\linkedin{adrian-k-h-lai}
\orcid{0000-0003-0446-119X}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``We are all in the gutter, but some of us are looking at the stars"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Adyen}
  {Amsterdam}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for R\&D Engineer II}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}%\today}
  {}%Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}


I am writing to express my strong interest in the R\&D Engineer II at ANSYS, as advertised on your company's website. With a background as a physicist working extensively in software development and a strong passion for pushing the boundaries of technology, I am excited about the prospect of contributing my skills to ANSYS's innovative projects.

My journey began in the realm of physics, where I gained proficiency in a range of technical areas, including C programming, Linux systems, supercomputing, and simulations. These skills have prepared me well for the role of a research software engineer, equipping me to take on complex technical challenges with confidence. Building upon this foundation, my PhD research took a unique trajectory by blending my expertise int the world of quantitative social sciences. During this time, I directed my efforts towards creating a sophisticated simulation framework and a game using Kotlin, tailored to study interstellar societies while considering relativistic physics — an endeavor that speaks to my ability to tackle intricate subject matter.

I am particularly proud of my accomplishments in designing and implementing this simulation framework. While Kotlin may not be the most performant choice, I invested significant effort in optimizing data structures and algorithms to ensure efficient execution and parallelizability. This project exemplifies my dedication to achieving high performance through meticulous software engineering.

Parallel to my academic pursuits, I have actively engaged with open-source projects, focusing predominantly on C++. These experiences have broadened my skill set, elevating me from a scientific programmer to a well-rounded software engineer. This transition underscores my commitment to excellence in software development and my readiness to adapt to new challenges.

Although my academic path has led me into interdisciplinary territory, I believe that my ability to quickly grasp and master new technical concepts, combined with my proficiency in collaboration, makes me a strong candidate for the R\&D Engineer II. The experience gained from working in diverse teams during my PhD research further bolsters my aptitude as a collaborative team player, an essential quality for success in ANSYS's dynamic environment.

As a Hong Kong citizen currently residing in the Netherlands, I am excited about the possibility of relocating to Canada under the open work permit policy. This aligns perfectly with my aspirations and eagerness to contribute to ANSYS's impactful projects.

Thank you for considering my application. I am enthusiastic about the prospect of joining ANSYS and contributing my unique blend of skills and experiences to the team. I look forward to the opportunity for further discussion in an interview setting.

%\lettersection{Why Me?}

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
