% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./profile}
\name{}{LAI Kwun Hang (Adrian)}
\position{Phd Candidate}
%\address{235, World Cup buk-ro, Mapo-gu, Seoul, 03936, Republic of Korea}

\mobile{(+31) 6-2184-1392}
\email{adrian.k.h.lai@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{Adriankhl}
\linkedin{adrian-k-h-lai}
\orcid{0000-0003-0446-119X}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``We are all in the gutter, but some of us are looking at the stars"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {The Hongkong and Shanghai Banking Corporation Limited}
  {Kowloon City, Hong Kong}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer - Digital Business Services}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}%\today}
  {}%Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing to express my genuine enthusiasm for the position of 'Software Engineer - Digital Business Services' at HSBC. Drawn by HSBC's outstanding reputation for technological innovation and global influence, I am excited about the opportunity to leverage my technical expertise to make a significant contribution to your esteemed team.

Having evolved from a background in physics, I have cultivated a comprehensive skill set that encompasses C, Python, Linux systems, supercomputing, and simulations. This diverse proficiency equips me to adeptly address complex technical challenges and provide robust solutions. My journey then took an intriguing turn during my PhD research, which fused my technical expertise with computational social sciences. Notably, my project on gender bias analysis in academic funding applications honed my prowess in SQL databases and programming languages such as Python, Julia, and Java.

A notable highlight of my journey was the creation of a game with advanced relativistic mechanics using Kotlin. This project entailed architecting the framework, optimizing algorithms, selecting suitable libraries, developing a code-generation plugin, providing comprehensive documentation for accessibility, and automating tests with JUnit and GitHub Actions. My expertise in mobile and Android development was demonstrated through a graphical interface for PC and Android, a client-server architecture for multiplayer functionality, and structured concurrency using kotlinx.coroutine. I proudly presented this work at esteemed conferences including FOSDEM and KotlinConf.

Complementing my academic journey, I have actively contributed to open-source projects, cultivating a diverse skill set that positions me as a versatile software engineer. This multifaceted experience showcases my commitment to excellence in software development and my agility in embracing novel challenges.

While my direct exposure to the financial sector may be limited, my educational background and wide-ranging experiences instill confidence in my capacity to swiftly grasp the intricacies of financial software. I am fully prepared to bridge any knowledge gaps, including those related to security aspects.

The innovative projects at HSBC seamlessly align with my aspirations, and I am eager to contribute my skill set effectively to your team. Thank you for considering my application. I eagerly anticipate the opportunity to further discuss how my distinctive background and experiences can complement HSBC's objectives.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
