% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
% -------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./profile}
\name{}{LAI Kwun Hang (Adrian)}
\position{Phd Candidate}
%\address{235, World Cup buk-ro, Mapo-gu, Seoul, 03936, Republic of Korea}

\mobile{(+852) 9171-2155 / (+31) 6-2184-1392}
\email{adrian.k.h.lai@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{Adriankhl}
\linkedin{adrian-k-h-lai}
\orcid{0000-0003-0446-119X}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``We are all in the gutter, but some of us are looking at the stars"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Maryknoll Fathers' School}
  {2 To Yuen Street, Tai Hang Tung, Kowloon, Hong Kong}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Mathematics Teacher (advertised on jump.mingpao.com)}
% How the letter is opened
\letteropening{Dear Principal Sung Hoi Yan,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}%\today}
  {}%Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing to express my strong interest in the ``Mathematics Teacher'' position at Maryknoll Fathers' School. With a deep passion for education and a solid academic background, I am excited about the opportunity to contribute to your school's mission.

I hold a master's degree and a bachelor's degree from the Chinese University of Hong Kong, majoring in physics and minoring in mathematics. Driven by my passion to apply scientific knowledge to make a positive impact on society, I decided to pursue a doctoral degree in quantitative social sciences at Leiden University in the Netherlands, where I am currently in the final stage of completion. During my doctoral studies, I developed a keen interest in education and even created an educational game to illustrate complex physics concepts, which further motivated me to return to Hong Kong and engage in secondary school teaching.

While I have not yet taught full-time in a secondary school, I have gained valuable teaching experience through various positions during my academic and youth service career. These opportunities have allowed me to work with individuals from diverse backgrounds, honing my ability to adapt my teaching methods and cater to the unique needs of students. Notably, my voluntary work with the Boy's Brigade has required me to establish strong relationships with secondary school students and provide them with academic guidance. I am confident that my experience and adaptability will enable me to create a positive and inclusive learning environment for students at your school.

As a quantitative social scientist, I have had plenty of exposure to real-world applications of mathematics and physics. While the specialized knowledge acquired through academic research may differ significantly from the content of secondary school textbooks, the curiosity, critical thinking skills, and data analysis abilities cultivated in research are invaluable assets. I am eager to guide students in developing these skills and instilling in them a lifelong passion for learning. Additionally, my participation in the International Physics Olympiad, where I proudly earned a silver medal, and my subsequent role as a mentor for the Hong Kong team have provided me with a unique perspective on mathematics and physics education. I am confident that I can provide additional mathematics, physics, and STEAM training, further enriching the educational experience of students.

Thank you for considering my application. I have attached my resume for your review. Currently, I am in Hong Kong to complete my thesis. I would be grateful for the opportunity to discuss my qualifications further.

%\lettersection{Why Me?}

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
