% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./profile}
\name{}{LAI Kwun Hang (Adrian)}
\position{Phd Candidate}
%\address{235, World Cup buk-ro, Mapo-gu, Seoul, 03936, Republic of Korea}

\mobile{(+852) 9171-2155 / (+31) 6-2184-1392}
\email{adrian.k.h.lai@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
\github{Adriankhl}
\linkedin{adrian-k-h-lai}
\orcid{0000-0003-0446-119X}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``We are all in the gutter, but some of us are looking at the stars"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Marymount Secondary School}
  {123 Blue Pool Road,Happy Valley, Hong Kong}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Mathematics Teacher (advertised on jump.mingpao.com)}
% How the letter is opened
\letteropening{Dear Principal Kyle Chan,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}%\today}
  {}%Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing to express my strong interest in the ``Mathematics Teacher'' position at Marymount Secondary School. As a researcher with a deep passion for education and being a Christian myself, I am excited to have the opportunity to teach in a Christian School.

I received a master's degree and a bachelor's degree from the Chinese University of Hong Kong, majoring in physics and minoring in mathematics. Driven by my passion for using knowledge of physics and mathematics to make a positive impact on society, I decided to pursue a doctoral degree in Social Sciences at Leiden University in the Netherlands, and I am currently in the final stage of completion. During my doctoral studies, I unexpectedly developed an educational game to illustrate complex physics concepts, which ignited my passion for teaching. This realization inspired me to transition my career back to Hong Kong, where I can share my knowledge and inspire secondary school students.

Although my teaching experience in secondary schools is limited, I have accumulated extensive teaching experience through various positions in academia. Besides, I actively participated in the youth work of the Boys' Brigade in Hong Kong, where I gained valuable experience in educating and managing secondary students. Furthermore, I have provided supplementary mathematics and physics tutorials to students seeking extra support, allowing me to refine my instructional skills. As a bonus, I represented Hong Kong in the 2012 International Physics Olympiad, where I proudly earned a silver medal. In 2016, I had the privilege of serving as a mentor for the Hong Kong team. I am confident in my ability to teach the core curriculum and provide additional mathematics, physics, and STEAM training to students.

While my specialized academic knowledge may differ from the content covered in secondary school textbooks, my interdisciplinary academic training has equipped me with a range of transferable skills. These skills enable me to understand and address the unique needs of both the school and its students. Furthermore, I firmly believe that the curiosity, critical thinking abilities, and data collection skills fostered through academic research are invaluable assets that can benefit students beyond their academic pursuits. I am eager to guide students in developing these aspects through my teaching and to create an engaging learning environment that promotes holistic growth.

As a devoted Christian, I embrace the significance of integrating faith into all aspects of our lives. Having actively participated in
local and international church communities, I understand the importance of promoting Christian values in the classroom. I am
committed to creating an environment where students can grow academically, morally, and spiritually.

Thank you for considering my application. I have attached my resume for your review. Currently, I am in Hong Kong to complete my thesis, and I would be grateful for the opportunity to discuss my qualifications further.

%\lettersection{Why Me?}

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
