% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
%\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Lai Kwun Hang (Adrian)} \\ \vspace{1pt}
    \small +852-9171-2155 $|$ \href{mailto:adrian.k.h.lai@gmail.com}{\underline{adrian.k.h.lai@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/adrian-k-h-lai}{\underline{linkedin.com/in/adrian-k-h-lai}} $|$
    \href{https://github.com/Adriankhl}{\underline{github.com/Adriankhl}}
\end{center}


%-----------EDUCATION-----------
\section{Summary}
Social science and physics researcher with a deep passion for education. 
Experienced in teaching both talented and underperforming students.
Dedicated to providing additional Physics Olympiad training and STEAM education.

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Leiden University}{Leiden, the Netherlands}
      {Ph.D. in Social Sciences (Quantitative Science Studies)}{Jun. 2019 -- present $|$ Expected graduation: 2024}
    \resumeSubheading
      {The Chinese University of Hong Kong}{Hong Kong, China}
      {M.Phil. in Physics, B.Sc. in Physics, minor in Mathematics}{Sep. 2012 -- Dec. 2018}
    \resumeSubheading
      {Shatin Pui Yin College}{Hong Kong, China}
      {HKDSE: Mathematics compulsory (5*) and Extended M2 (5*), Physics (5)}{Sep. 2006 -- Aug. 2012}
  \resumeSubHeadingListEnd

\section{Qualifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Basic Law and National Security Law Test (Degree/Professional Grades)}{: Pass}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Researcher/Ph.D. Candidate}{Leiden, the Netherlands}
      {Leiden University}{Jun. 2019 -- present}
      \resumeItemListStart
        \resumeItem{Developed an educational game to illustrate physics concepts effectively}
        \resumeItem{Presented the game and other research findings at various international conferences}
        \resumeItem{Designed mathematics and IT training courses for non-technical individuals}
        \resumeItem{Conducted workshops on open science in collaboration with library staff}
      \resumeItemListEnd
      
    \resumeSubheading
      {Officer}{Hong Kong, China}
      {The Boy's Brigade}{Sep. 2012 -- Aug. 2018}
      \resumeItemListStart
        \resumeItem{Organized and delivered diverse courses covering natural sciences and practical skills}
        \resumeItem{Provided tutorials in mathematics and physics to HKDSE students}
        \resumeItem{Led foot drill training for secondary school students, fostering teamwork and discipline among participants}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{Hong Kong, China}
      {The Chinese University of Hong Kong}{Sep. 2016 - Feb. 2018}
      \resumeItemListStart
        \resumeItem{Prepared and delivered tutorials for undergraduate students}
        \resumeItem{Provided one-on-one consultations, guiding underperforming students towards improvement}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{Hong Kong, China}
      {Hong Kong Baptist University}{Aug. 2015 -- May. 2016}
      \resumeItemListStart
        \resumeItem{Organized training sessions for talented secondary school students}
        \resumeItem{Led the Hong Kong team in the Asian Physics Olympiad 2016, achieving commendable results}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Special Secondary School Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Physics Olympiad}{Estonia}
      {Silver Medallist}{2012}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{HKDSE}{: Mathematics, Mathematics Module 2, Physics, Science} \\
     \textbf{STEAM}{: Software engineering, Data analysis, Research (Mathematics, Physics, Computational Social Science)}
     \textbf{Languages}{: Cantonese (Native), English (Fluent), Putonghua (Fluent)} \\
     \textbf{Music}{: Violin}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
