% arara: lualatex
% arara: clean: { extensions: [ acn,acr,alg,aux,bbl,bcf,blg,glg,glo,gls,idx,ilg,ind,ist,log,lof,lol,lot,out,ptc,toc,run.xml ]}

%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
%\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Lai Kwun Hang (Adrian)} \\ \vspace{1pt}
    \small +852-9171-2155 $|$ \href{mailto:adrian.k.h.lai@gmail.com}{\underline{adrian.k.h.lai@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/adrian-k-h-lai}{\underline{linkedin.com/in/adrian-k-h-lai}} $|$
    \href{https://github.com/Adriankhl}{\underline{github.com/Adriankhl}}
\end{center}


%-----------EDUCATION-----------
\section{Summary}
Software developer and researcher with a robust background in physics and computational social science. Skilled in developing complex software solutions and conducting data-oriented research.

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Leiden University}{Leiden, the Netherlands}
      {Ph.D. in Quantitative Science Studies}{Jun. 2019 -- present $|$ Expected graduation: 2024}
    \resumeSubheading
      {The Chinese University of Hong Kong}{Hong Kong, China}
      {M.Phil. in Physics, B.Sc. in Physics, minor in Mathematics}{Sep. 2012 -- Dec. 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Indie game developer}{Leiden, the Netherlands}
      {Self-employment}{Mar. 2022 -- present}
      \resumeItemListStart
        \resumeItem{Developed a turn-based strategy game in Kotlin, incorporating sophisticated relativistic physics.}
        \resumeItem{Managed a codebase with over 60K lines of code using Git.}
        \resumeItem{Presented at various conferences, including KotlinConf and FOSDEM.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Researcher}{Leiden, the Netherlands}
      {Research on Research Institute (RORI)}{Jan. 2020 -- present}
      \resumeItemListStart
        \resumeItem{Collaborated with an international team spanning 5 countries}
        \resumeItem{Worked with software developers to build a data platform for confidential funding data}
        \resumeItem{Conducted data-oriented research on funding allocation dynamics}
        \resumeItem{Organized training workshops on open science and open source practices}
    \resumeItemListEnd

    \resumeSubheading
      {Researcher}{Hong Kong, China}
      {LIGO Scientific Collaboration (LSC)}{Sep. 2016 -- Aug. 2018}
      \resumeItemListStart
        \resumeItem{Proposed models to detect black-hole horizon effects and gravitational wave lensing.}
        \resumeItem{Ran simulations on supercomputer clusters.}
        \resumeItem{Conducted Bayesian statistical analysis on simulated and real data using Python.}
        \resumeItem{Published 2 papers in reputable journals.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Godot LLM} $|$ \href{https://github.com/Adriankhl/godot-llm}{\underline{GitHub}} $|$ \emph{C++, SQL, GDScript}}{Apr. 2024 -- present}
          \resumeItemListStart
            \resumeItem{Integrated local large language models with multimodal input into the Godot game engine.}
            \resumeItem{Developed a retrieval-augmented generation framework based on SQLite.}
            \resumeItem{Provided demos and authored detailed documentation.}
            \resumeItem{Supported users on GitHub and Discord.}
            \resumeItem{Contributed bug fixes to upstream libraries.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Relativitization} $|$ \href{https://github.com/Adriankhl/relativitization}{\underline{GitHub}} $|$ \emph{Kotlin, Ktor, kotlinx.coroutine, Gradle, Python}}{Mar. 2021 -- present}
          \resumeItemListStart
            \resumeItem{Developed a parallel agent-based computational framework utilizing coroutines.}
            \resumeItem{Designed efficient algorithms and data structures for relativistic spacetime calculations.}
            \resumeItem{Automated testing using JUnit and GitHub Actions.}
            \resumeItem{Authored comprehensive documentation.}
            \resumeItem{Built models and a game using the framework.}
            \resumeItem{Published 2 papers on the framework and model.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Funding criteria and gender biases} $|$ \emph{Python, PyStan, pandas, SQL}}{Jan. 2020 -- May. 2022}
          \resumeItemListStart
            \resumeItem{Collaborated with domain experts to formulate causal relations}
            \resumeItem{Designed and implemented Bayesian network models to identify gender biases in funding schemes}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Kotlin, Java, SQL, Python, Julia, C/C++, Bash, LaTeX} \\
     \textbf{Tools and Libraries}{: Git, Linux, Godot, kotlinx.coroutine, pandas, NumPy} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
